---
output: 
  github_document:
    toc: true
  
title: "Quick Summary Statistics for Data Frames Package"
author: "Maddy Riddler"
---

```{r setup, include=FALSE}
library(testthat)
```

# quickstats

## Description

> The quickstats package provides tools for quickly calculating useful summary statistics for all numeric variables in a data frame. It includes functions for handling missing values and generating comprehensive statistical summaries. The main function, quickstats(), allows users to calculate various statistics such as mean, standard deviation, median, mode, and range for numeric columns in a given data frame. Installation You can install the development version of quickstats from GitHub with:

```{r}
# install.packages("devtools")
devtools::install_github("stat545ubc-2024/quickstats")
```

## Usage

> Here are some examples of how to use the quick_stats() function:

```{r}
library(quickstats)

# Calculate all statistics for mtcars dataset
quickstats(mtcars)

# Handle dataset with no numeric columns
quickstats(data.frame(a = c("x", "y", "z"), b = c("a", "b", "c")))
```

## Tests

### NA vectors

```{r}
test_that("quickstats handles vectors with NA values correctly", {
  test_data <- data.frame(x = c(1, 2, NA, 4, 5))
  result <- quickstats(test_data)
  expect_s3_class(result, "tbl_df")
  expect_equal(result$mean, 3)
  expect_equal(result$sd, sd(c(1, 2, 4, 5), na.rm = TRUE))
  expect_equal(result$median, 3)})
```

### Non-numeric vectors

```{r}
test_that("quickstats handles non-numeric data correctly", {
  test_data <- data.frame(x = c("a", "b", "c", "d", "e"))
  expect_message(result <- quickstats(test_data), "No numeric columns found")
  expect_null(result)
  test_data_factor <- data.frame(x = factor(c("low", "medium", "high", "low", "high")))
  expect_message(result_factor <- quickstats(test_data_factor), "No numeric columns found")
  expect_null(result_factor)})
```

### No NA vectors

```{r}
test_that("quickstats handles data with no NA values correctly", {
  test_data <- data.frame(x = 1:5, y = 6:10)
  result <- quickstats(test_data)
  expect_no_error(quickstats(test_data))
  expect_equal(nrow(result), ncol(test_data))
 expect_equal(result$variable, c("x", "y"))})
```
