---
output: 
  github_document:
    toc: true
  
title: "Quick Summary Statistics for Data Frames Package"
author: "Maddy Riddler"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(devtools)
library(magrittr)
library(rlang)
library(tidyverse)
library(roxygen2)
library(testthat)
```

# quickstats

## Description

> The quickstats package provides tools for quickly calculating useful summary statistics for all numeric variables in a data frame. It includes functions for handling missing values and generating comprehensive statistical summaries. The main function, quick_stats(), allows users to calculate various statistics such as mean, standard deviation, median, mode, and range for numeric columns in a given data frame. Installation You can install the development version of quickstats from GitHub with:

```{r}
# install.packages("devtools")
devtools::install_github("maddyriddler/assignment-b2-maddyriddler", build_vignettes = FALSE, ref = "0.1.1")
```

## Usage

> Here are some examples of how to use the quick_stats() function:

```{r}
library(quickstats)

# Calculate all statistics for mtcars dataset
quick_stats(mtcars)

# Calculate only mean and median, return as list
quick_stats(mtcars, stats = c("mean", "median"), as_list = TRUE)

# Handle dataset with no numeric columns
quick_stats(data.frame(a = c("x", "y", "z"), b = c("a", "b", "c")))
```
